### 2023-04-04 outputs/paper/paper.qmd
Graphs from Fashion Datasets

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Huda Sahaf
thanks: "Code and data are available at: LINK."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(janitor)
library(dplyr)
library(ggplot2)
library(kableExtra)
library(knitr)
library(RColorBrewer)
```

```{r}
### Clean Fashion Tones Dataset: 
cleaned_fashion_tones <-
  clean_names(fashion_tones)

cleaned_fashion_tones <-
  cleaned_fashion_tones |>
  rename(
    skintone = tone,
    lightness_value = l
  )
head(cleaned_fashion_tones)
```

```{r}
### Simplifying Dates: Fashion Tones Dataset:
cleaned_fashion_tones<-
  cleaned_fashion_tones |>
  separate(
    col = date,
    into = c("Month", "Day", "Year"),
    sep = "/"
  ) |>
  select(-Day)|>
  mutate(cleaned_fashion_tones, Date = paste(Year, Month, sep = "-"))

```

```{r}
### Modeling Full Spread of Complexion Values on Vogue Covers from 2000-2018
cleaned_fashion_tones |>
  ggplot(aes(x = lightness_value, y = Date)) +
  geom_point(aes(color = lightness_value < 0.4)) +
  theme_classic() +
  labs(
    x = "Lightness Value of the Models",
    y = "Date of Cover",
    title = "Complexions of Models on Covers of Vogue: 2000-2018"
  )

```

```{r}
### Clean Fashion Frequency Data Set: 
cleaned_fashion_frequency<-
  clean_names(fashion_frequency)

cleaned_fashion_frequency <-
  cleaned_fashion_frequency |>
  rename(
    skintone = tone,
    lightness_value = l,
    num_covers = n_covers
  )

```

```{r}
### Table 1: All Models With More than 5 Appearances on Vogue 
cleaned_fashion_frequency |>
  select(model, num_covers, lightness_value) |>
  group_by(num_covers) |>
  filter(num_covers > 4) |>
  kable(
    col.names = c(
      "Model",
      "Number of Covers", 
      "Lightness Value"
    ),
    digits = 2
  )

```

```{r}
### Graph 2: Case Study: Rihanna's 5 Appearances and the respective Complexion Values:
cleaned_fashion_tones|>
  group_by(model)|>
  filter(model=="Rihanna")|>
  ggplot(mapping = aes(x = Year, y = lightness_value, color = model)) +
  geom_point()+
  labs(
    title = "Rihanna: A Case Study in White-Washing",
    y = "Complexion Value",
    color = "Model"
  )

```

```{r}
### Graph 3: The Top 4 Deepest Complexion Models on Vogue
cleaned_fashion_tones|>
  filter(model== "Lupita Nyongo" | model=="Rihanna"| model == "Michelle Obama" | model == "Serena Williams") |>
  ggplot(aes(y = lightness_value, color = model)) +
  geom_boxplot() +
  theme_light() +
  labs(
    y = "Lightness Value of Skintone",
    title = "Appearances of Deepest Complexion Models on Vogue"
  )
```

```{r}
### Graph 4: Models with the Highest Number of Appearances on Vogue and their respective Complexion Values
cleaned_fashion_tones|>
  filter(model== "Nicole Kidman" | model=="Gisele Bundchen"| model == "Charlize Theron" | model == "Sarah Jessica Parker") |>
  ggplot(aes(y = lightness_value, color = model)) +
  geom_boxplot() +
  theme_light() +
  labs(
    y = "Lightness Value of Skintone",
    title = "Complexions of Models with Highest Number of Vogue Covers" 
  )

```

```{r}

```

# Introduction

You can and should cross-reference sections and sub-sections. For instance, @sec-data and @sec-first-point.

# Data {#sec-data}

Our data is of penguins (@fig-bills).

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

Also bills and their average (@fig-billssssss). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work.)

```{r}
#| label: fig-billssssss
#| fig-cap: More bills of penguins
#| echo: false
#| fig-width: 8
#| fig-height: 4

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk way more about it.

# Model

$$
Pr(\theta | y) = \frac{Pr(y | \theta) Pr(\theta)}{Pr(y)}
$$ {#eq-bayes}

@eq-bayes seems useful, eh?

Here's a dumb example of how to use some references: In paper we run our analysis in `R` [@citeR]. We also use the `tidyverse` which was written by @thereferencecanbewhatever If we were interested in baseball data then @citeLahman could be useful.

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional details

\newpage

# References

### 2023-04-04 outputs/paper/paper.qmd
Graphs and Tables of Makeup dataset

@@
 ```{r}
+#| include: false
+#| warning: false
+#| echo: false
+#| message: false
+
 ### Clean Fashion Tones Dataset: 
@@
 ```{r}
+#| include: false
+#| warning: false
+#| echo: false
+#| message: false
+
 ### Simplifying Dates: Fashion Tones Dataset:
@@
 ```{r}
-### Modeling Full Spread of Complexion Values on Vogue Covers from 2000-2018
-cleaned_fashion_tones |>
-  ggplot(aes(x = lightness_value, y = Date)) +
-  geom_point(aes(color = lightness_value < 0.4)) +
-  theme_classic() +
-  labs(
-    x = "Lightness Value of the Models",
-    y = "Date of Cover",
-    title = "Complexions of Models on Covers of Vogue: 2000-2018"
-  )
+#| include: false
+#| warning: false
+#| echo: false
+#| message: false
 
-```
-
-```{r}
 ### Clean Fashion Frequency Data Set: 
@@
 ```{r}
+#| include: false
+#| warning: false
+#| echo: false
+#| message: false
+
+### Clean Makeup Shades Data Set:
+cleaned_makeup_shades <-
+  clean_names(makeup_shades)
+
+cleaned_makeup_shades<-
+  cleaned_makeup_shades |>
+  rename(
+    hue = h,
+    lightness = l,
+    saturation = s,
+    value = v,
+    hex_code = hex
+  )|>
+  mutate(lightness_value = lightness/100)
+
+cleaned_makeup_shades<-
+  cleaned_makeup_shades |>
+  filter(group == 0|group == 1|group == 2|group == 3|group == 4)
+
+```
+
+```{r}
+#| warning: false
+#| echo: false
+#| label: fig-fullspread
+#| fig-cap: Complexion Values of All Models on Vogue Covers from 2000-2018
+### Modeling Full Spread of Complexion Values on Vogue Covers from 2000-2018
+cleaned_fashion_tones |>
+  ggplot(aes(x = lightness_value, y = Date)) +
+  geom_point(aes(color = lightness_value < 0.4)) +
+  theme_classic() +
+  labs(
+    x = "Lightness Value of the Models",
+    y = "Date of Cover",
+    title = "Complexions of Models on Covers of Vogue: 2000-2018"
+  )
+
+```
+
+```{r}
+#| message: false
+#| warning: false
+#| echo: false
+#| tbl-cap: "Models With More than 5 Appearances on Vogue"
+#| label: tbl-appearances
 ### Table 1: All Models With More than 5 Appearances on Vogue 
@@
 ```{r}
+#| warning: false
+#| echo: false
+#| label: fig-whitewashing
+#| fig-cap: Rihanna's Appearances on Vogue
 ### Graph 2: Case Study: Rihanna's 5 Appearances and the respective Complexion Values:
@@
 ```{r}
+#| warning: false
+#| echo: false
+#| label: fig-deepest
+#| fig-cap: Top 4 Deepest Complexion Models on Vogue
 ### Graph 3: The Top 4 Deepest Complexion Models on Vogue
@@
 ```{r}
+#| warning: false
+#| echo: false
+#| label: fig-all_white
+#| fig-cap: Models with Highest Number of Appearances
 ### Graph 4: Models with the Highest Number of Appearances on Vogue and their respective Complexion Values
@@
 ```{r}
+#| message: false
+#| warning: false
+#| echo: false
+#| tbl-cap: "US Makeup Brands: Foundation Shade Range"
+#| label: tbl-shades
+
+### Table 2: All US Brands and Their Number of Foundation Shades
+cleaned_makeup_shades|>
+  select(brand, product, lightness_value)|>
+  group_by(brand) |>
+  summarise(total_shades = n()) |>
+  kable(
+    col.names = c(
+      "Makeup Brand",
+      "Number of Foundation Shades"
+      )
+  )
+
+```
+
+```{r}
+#| warning: false
+#| echo: false
+#| label: fig-bestsellers
+#| fig-cap: The Shade Distribution of Best-Selling Foundations in the U.S
+### Graph 5: US Bestseller Foundations and Their Inclusivity 
+cleaned_makeup_shades|>
+  filter(group == 2)|>
+  group_by(brand)|>
+  ggplot(aes(x = lightness_value, color = brand)) +
+  stat_ecdf(geom = "point") +
+  theme_classic()
+
+```
+
+```{r}
+#| warning: false
+#| echo: false
+#| label: fig-bipoc
+#| fig-cap: The Shade Distribution of BiPOC-owned Makeup Brands
+### Graph 5: BiPOC Reccs of Brands with BiPOC Founder Bestseller Foundations and Their Inclusivity 
+cleaned_makeup_shades|>
+  filter(group == 3)|>
+  group_by(brand)|>
+  ggplot(aes(x = lightness_value, color = brand)) +
+  stat_ecdf(geom = "point") +
+  theme_classic()
+```
+
+```{r}
+#| warning: false
+#| echo: false
+#| label: fig-bigboys
+#| fig-cap: The Shade Distribution of Largest Shade Ranges Offered in the U.S
+### Graph Range of Shades With Brands with Largest Shade Ranges
+cleaned_makeup_shades|>
+  filter(brand == "Beauty Bakerie"|brand == "Bobbi Brown" |brand == "bareMinerals" |brand == "Bobbi Brown" | brand == "MAC"| brand == "Maybelline"|brand == "Estée Lauder"|brand == "Fenty"|brand == "Lancôme"|brand == "Make Up For Ever")|>
+  ggplot(cleaned_makeup_shades, mapping = aes(x = brand, y = lightness_value)) + 
+  geom_boxplot() +
+  geom_jitter(alpha = 0.3, width = 0.15, height = 0) +
+  theme_minimal()
 

### 2023-04-04 outputs/paper/paper.qmd
added abstract

@@
 date-format: "D MMMM YYYY"
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "This paper aims to investigate the history of racism in the beauty industry and how this impacts the inclusivity in the market.
+The complexions of models are assigned a lightness value and analyzed across 8 years.
+These results are compared to the foundation shade ranges across all major makeup brands across the U.S revealing a continuation of compounding racism within the industry as a whole."
 format: pdf

### 2023-04-05 outputs/paper/paper.qmd
Forced it to render as a pdf

@@
 ---
-title: "My title"
-subtitle: "My subtitle if needed"
+title: "The Shades of Racism in the Beauty Industry"
+subtitle: "An exploration of inclusivity and tokenism within fashion and makeup"
 author: 
@@
 library(knitr)
+library(readr)
 library(RColorBrewer)
@@
 ```{r}
-#| include: false
-#| warning: false
-#| echo: false
-#| message: false
+fashion_tones <-
+  read.csv(
+    file = "https://raw.githubusercontent.com/the-pudding/data/master/vogue/faces.csv", 
+    skip = 0 
+  )
+
+fashion_frequency <-
+  read.csv(
+    file = "https://raw.githubusercontent.com/the-pudding/data/master/vogue/models.csv", 
+    skip = 0 
+  )
+
+makeup_shades <-
+  read.csv(
+    file = "https://raw.githubusercontent.com/the-pudding/data/master/makeup-shades/shades.csv", 
+    skip = 0 
+  )
+
+#### Save data ####
+
+write_csv(fashion_tones, here::here("inputs/data/fashion_tones.csv"))
+
+write_csv(fashion_frequency, here::here("inputs/data/fashion_frequency.csv"))
+
+write_csv(makeup_shades, here::here("inputs/data/makeup_shades.csv"))
+
+```
+
+```{r}
 
@@
 #| echo: false
-
-ggplot(penguins, aes(x = island, fill = species)) +
-  geom_bar(alpha = 0.8) +
-  scale_fill_manual(values = c("darkorange","purple","cyan4"),
-                    guide = "none") +
-  theme_minimal() +
-  facet_wrap(~species, ncol = 1) +
-  coord_flip()
 ```
@@
 (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work.)
-
-```{r}
-#| label: fig-billssssss
-#| fig-cap: More bills of penguins
-#| echo: false
-#| fig-width: 8
-#| fig-height: 4
-
-ggplot(penguins, aes(x = island, fill = species)) +
-  geom_bar(alpha = 0.8) +
-  scale_fill_manual(values = c("darkorange","purple","cyan4"),
-                    guide = "none") +
-  theme_minimal() +
-  facet_wrap(~species, ncol = 1) +
-  coord_flip()
-```
 

### 2023-04-05 outputs/paper/paper.qmd
Added github repo link

@@
   - Huda Sahaf
-thanks: "Code and data are available at: LINK."
+thanks: "Code and data are available at: https://github.com/hsahaf/Racism_Beauty_Industry.git."
 date: "`r Sys.time()`"

### 2023-04-17 outputs/paper/paper.qmd
cleaned dates and added references

@@
 library(RColorBrewer)
+library(scales)
 ```
@@
   ) |>
-  select(-Day)|>
-  mutate(cleaned_fashion_tones, Date = paste(Year, Month, sep = "-"))
+  mutate(cleaned_fashion_tones, clean_date = paste(Year, Month, Day, sep = "-"))
+  str(cleaned_fashion_tones$clean_date)
 
@@
 ```{r}
-#| warning: false
-#| echo: false
 #| label: fig-fullspread
@@
 ### Modeling Full Spread of Complexion Values on Vogue Covers from 2000-2018
-cleaned_fashion_tones |>
-  ggplot(aes(x = lightness_value, y = Date)) +
+cleaned_fashion_tones$clean_date <- ymd(cleaned_fashion_tones$clean_date)
+
+entire_spread <- cleaned_fashion_tones |>
+  ggplot(aes(x = lightness_value, y = clean_date)) +
   geom_point(aes(color = lightness_value < 0.4)) + 
-  theme_classic() +
   labs(
-    x = "Lightness Value of the Models",
+    x = "Lightness Value of Vogue Models",
     y = "Date of Cover",
     title = "Complexions of Models on Covers of Vogue: 2000-2018"
-  )
+  ) +
+  theme_classic()
 
+datebreaks <- seq(as.Date("2001-01-01"), as.Date("2018-09-01"), by = "1 year")
+
+print(entire_spread)
 ```
+
+@fig-fullspread is a graph of the lightness value of every model that has been on the cover of Vogue from 2000 to 2018. Lightness value is
 
@@
 
+## Data Management
+In order to conduct an analysis on the various parts of the beauty industry, three separate datasets were used. The Pudding is a digital publication that makes its data sets open to the public @pudd.
+This paper utilizes the 
 Our data is of penguins (@fig-bills).

### 2023-04-18 outputs/paper/paper.qmd
Added data section

@@
 # Data {#sec-data}
+## Data Management
+All analysis on the data sets were done using R [@citeR].
+The data was read in, cleaned, and manipulated using `dplyr`[@dan], `tidyverse` [@tidy], and `janitor` [@janice].
+The graphs and tables in this paper were coded using the following packages: `ggplot2` [@gabe], `kableExtra`[@kev], `knitr` [@nat], `readr` [@ron], and `RColorBrewer`[@ryan].
 
-## Data Management
-In order to conduct an analysis on the various parts of the beauty industry, three separate datasets were used. The Pudding is a digital publication that makes its data sets open to the public @pudd.
-This paper utilizes the 
+## Source and Sampling
+In order to conduct an analysis on the various parts of the beauty industry, three separate data sets were used.
+The Pudding is a digital publication that makes its data sets open to the public @pudd.
+A closer look is taken at Vogue using the first two data sets used for the article *Colorism in High Fashion* [@high_f].
+All covers of Vogue from the year 2000 to 2018 are analyzed and categorized in these data sets.
+The female models on each cover are identified, and then their skin tones are filtered out of the cover, and an average color value is assigned based on the all skin tone pixels.
+These color values are then drained of any hue or saturation and therefore assigned a lightness value based on how light or deep the complexion of the model is, which allows for the comparison of all models on the covers of Vogue over the span of 8 years.
+The first data set contains the name of the model, date of their appearance on Vogue, the hex code of their skin tone, and their lightness value once the hue and saturation has been removed.
+This includes multiple appearances of the same model.
+The second data set contains the names of the models, the hex code of their skin tone, the number of covers they have made appearances in, and their average lightness value across these appearances.
+
+The data set behind The Pudding article, *Beauty Brawl* is the third data set used in this paper [@bbshades].
+It contains data about the foundation shade ranges through lightness values of multiple beauty brands around the world.
+For the sake of this paper, we are focusing on beauty retailers based in the US, especially since Vogue is also based in the United States.
+
 Our data is of penguins (@fig-bills).
@@
 Talk way more about it.
-
-# Model
-
-$$
-Pr(\theta | y) = \frac{Pr(y | \theta) Pr(\theta)}{Pr(y)}
-$$ {#eq-bayes}
-
-@eq-bayes seems useful, eh?
 

### 2023-04-18 outputs/paper/paper.qmd
fixed previous citation issues
Added descriptions of graphs, and more references

@@
 ```{r}
+#| message: false
+#| warning: false
+#| echo: false
 #| label: fig-fullspread
@@
 ```
-
-@fig-fullspread is a graph of the lightness value of every model that has been on the cover of Vogue from 2000 to 2018. Lightness value is
 
@@
 ```
-
 ```{r}
@@
 #| fig-cap: The Shade Distribution of BiPOC-owned Makeup Brands
-### Graph 5: BiPOC Reccs of Brands with BiPOC Founder Bestseller Foundations and Their Inclusivity 
+### Graph 5: BiPOC Recomendations of Brands with BiPOC Founder Bestseller Foundations and Their Inclusivity 
 cleaned_makeup_shades|>
@@
 
-Our data is of penguins (@fig-bills).
-
 ```{r}
@@
 
-Talk more about it.
+# Results
+@fig-fullspread is a graph of the lightness value of every model that has been on the cover of Vogue from 2000 to 2018.
+Lightness value is measured on a scale from 0 to 1, 1 being extremely pale in skin tone, and 0 being extremely deep.
+There is a general trend present almost immediately, in that across the entire 8 year period, Vogue has consistently had lighter skinned individuals with a lightness value of 0.5 to 0.8 on their covers.
+It has only been after around 2009 that we see a model on Vogue with a complexion deeper than 0.4.
 
-Also bills and their average (@fig-billssssss).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work.)
+@tbl-appearances is a table of all the models on Vogue who have had more than 4 appearances on the covers of Vogue between 2000 and 2018.
+In all of the names on this list, Rihanna is the only black woman, and her average lightness value across these five appearances has been fairly midtoned, at a lightness value of 0.62.
 
-Talk way more about it.
+@fig-whitewashing takes a closer look at Vogue's presentation of Rihanna's skintone on her five appearances.
+Vogue has been publicly accused of whitewashing Rihanna's complexion on some of her covers, and it is apparent that only after 2016 does her lightness value drop below 0.4 [@whitewashed].
+While lighting and editing can account for some fluctuations in the lightness value, but it does not explain the extent of the contrast between her first three appearances and her most recent two.
 
-Here's a dumb example of how to use some references: In paper we run our analysis in `R` [@citeR].
-We also use the `tidyverse` which was written by @thereferencecanbewhatever If we were interested in baseball data then @citeLahman could be useful.
+@fig-deepest takes a closer look at the fluctuations in lightness values in the appearances on the models with the deepest complexions on Vogue.
+Rihanna has had the highest number of appearances at 5 total covers from 2000 to 2018, followed by Lupita Nyongo, at 4.
+Amongst these models, Lupita Nyongo has the deepest complexion and her appearances on Vogue are the most recent, her last two being in 2015 and in 2018.
+The fluctuation is apparent in her appearances as well, in that it is only in her most recent cover that her lightness value is shown to be deeper than 0.3.
 
-We can use maths by including latex between dollar signs, for instance $\theta$.
+@fig-all_white shows the fluctuation in the lightness values of the top four models with the greatest number of covers on Vogue.
+All four of these models are white, and all of them have made appearances in 6 or more covers.
+Vogue's preferences for tanned white women is clear in that in the span of 8 years, the lightness value rarely drops below 0.6.
 
-# Results
+@tbl-shades is a table of all of the major beauty brands that are based in the United States, and the number of shades in their main foundation line.
+
+@fig-bestsellers takes a closer look at the inclusivity of the bestselling foundation lines across some of the largest beauty brands across the United States of America.
+It is clear that there are a greater number of shades available for people with lighter skin tones, with a lightness value of 0.6 or lighter, across all of the major brands.
+However, for people with a complexion that is a hair deeper than a medium skin tone, the number of shades become sparse, and the distribution spreads out as the lightness value becomes deeper than 0.5.
+
+@fig-bipoc looks at the shade distributions of the retailers with owners that are black, indigenous, or other people of color.
+The distribution is much more even, and all of these beauty brands provide options for people that are on both sides of the spectrum, complexions with lightness values deeper than 0.3, as well as complexions with lightness values paler than 0.8.
+
+@fig-bigboys looks at the distribution across the beauty brands based in the United States with a foundation line with more than 25 shades.
+The contrast between the number of shades provided for people with light to medium complexions (0.6-1) and the lack thereof in terms of the number of shades for people with deeper complexions (0-0.35) is apparent.
 

### 2023-04-18 outputs/paper/paper.qmd
hide code

@@
 title: "The Shades of Racism in the Beauty Industry"
-subtitle: "An exploration of inclusivity and tokenism within fashion and makeup"
+subtitle: "An exploration of inclusivity and tokenism within fashion and makeup industries"
 author: 
@@
 ```{r}
+#| include: false
+#| warning: false
+#| message: false
 fashion_tones <-
@@
 ```{r}
-
+#| include: false
+#| warning: false
+#| message: false
 ### Clean Fashion Tones Dataset: 

### 2023-04-18 outputs/paper/paper.qmd
first discussion point

@@
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+The same trend exists across the entire beauty industry.
+The deeper your complexion, the less options there are available for you.
+There are far less doors open for people of color in the beauty space, which causes several issues to compound.
+There is intersectionality at present in the communities of people impacted by this cycle of racism.
+Not only are these individuals at a disadvantage in society because they are women, but the issues are compounded further if they are individuals of color.
+These industries feed into each other, the less representation there is for black and brown women in fashion, the less options will be made available in the beauty industry and vice versa.
+The lack of representation creates a scarcity mindset.
+These women feel like they are the exception rather than the norm, and without the options available, without the same advantage of seeing people like you succeed, you are less likely to feel safe in these spaces and less confident when it comes to seeking to be in them.
+But the presence of black and brown women in these spaces has a significant impact.
+An example of this is in the beauty industry.
+The 'Pull Up or Shut Up' movement in 2020 forced beauty brands to reveal how many BiPOC women were staff members and in senior leadership positions[@pullup].
+It pushed for transparency in their marketing claims and resulted in a significant increase in consumer awareness, customers were now able to support brands that supported them.
+However, the same cannot be said for the fashion industry.
+The beauty industry is a commercial space that is not as difficult to break into through the rise of beauty influences, but high fashion is still considered to be a very elitist institution.
+BiPOC women have the power to revolutionize the beauty industry as a whole, but the lack of representation makes the path significantly harder.
+The compounding racism bleeds into other industries as well, such as television and film, and which hurts young girls the most.
+Looking into a world that has not made any room for you can be a very difficult and disheartening thing to overcome for children.
+Despite claims made by major institutions, this data reveals that it is only recently that black and brown women have been able to break into the industry, and it still has a long way to go in terms of actually uplifting and empowering them.
 
@@
 
-\appendix
-
-# Appendix {-}
-
-# Additional details
-
-\newpage
-
 # References

### 2023-04-19 outputs/paper/paper.qmd
Updated scripts 01 and 02

@@
 #| message: false
-fashion_tones <-
-  read.csv(
-    file = "https://raw.githubusercontent.com/the-pudding/data/master/vogue/faces.csv", 
-    skip = 0 
-  )
-
-fashion_frequency <-
-  read.csv(
-    file = "https://raw.githubusercontent.com/the-pudding/data/master/vogue/models.csv", 
-    skip = 0 
-  )
-
-makeup_shades <-
-  read.csv(
-    file = "https://raw.githubusercontent.com/the-pudding/data/master/makeup-shades/shades.csv", 
-    skip = 0 
-  )
-
-#### Save data ####
-
-write_csv(fashion_tones, here::here("inputs/data/fashion_tones.csv"))
-
-write_csv(fashion_frequency, here::here("inputs/data/fashion_frequency.csv"))
-
-write_csv(makeup_shades, here::here("inputs/data/makeup_shades.csv"))
+# fashion_tones <-
+#   read.csv(
+#     file = "https://raw.githubusercontent.com/the-pudding/data/master/vogue/faces.csv", 
+#     skip = 0 
+#   )
+# 
+# fashion_frequency <-
+#   read.csv(
+#     file = "https://raw.githubusercontent.com/the-pudding/data/master/vogue/models.csv", 
+#     skip = 0 
+#   )
+# 
+# makeup_shades <-
+#   read.csv(
+#     file = "https://raw.githubusercontent.com/the-pudding/data/master/makeup-shades/shades.csv", 
+#     skip = 0 
+#   )
+# 
+# #### Save data ####
+# 
+# write_csv(fashion_tones, here::here("inputs/data/fashion_tones.csv")) 
+# 
+# write_csv(fashion_frequency, here::here("inputs/data/fashion_frequency.csv")) 
+# 
+# write_csv(makeup_shades, here::here("inputs/data/makeup_shades.csv"))
 
@@
 ### Clean Fashion Tones Dataset: 
-cleaned_fashion_tones <-
-  clean_names(fashion_tones)
-
-cleaned_fashion_tones <-
-  cleaned_fashion_tones |>
-  rename(
-    skintone = tone,
-    lightness_value = l
-  )
-head(cleaned_fashion_tones)
+# cleaned_fashion_tones <-
+#   clean_names(fashion_tones)
+# 
+# cleaned_fashion_tones <-
+#   cleaned_fashion_tones |>
+#   rename(
+#     skintone = tone,
+#     lightness_value = l
+#   )
+# head(cleaned_fashion_tones)
 ```
@@
 
-### Simplifying Dates: Fashion Tones Dataset:
-cleaned_fashion_tones<-
-  cleaned_fashion_tones |>
-  separate(
-    col = date,
-    into = c("Month", "Day", "Year"),
-    sep = "/"
-  ) |>
-  mutate(cleaned_fashion_tones, clean_date = paste(Year, Month, Day, sep = "-"))
-  str(cleaned_fashion_tones$clean_date)
+### Simplifying Dates: Fashion Tones Data Set:
+# cleaned_fashion_tones<-
+#   cleaned_fashion_tones |>
+#   separate(
+#     col = date,
+#     into = c("Month", "Day", "Year"),
+#     sep = "/"
+#   ) |>
+#   mutate(cleaned_fashion_tones, clean_date = paste(Year, Month, Day, sep = "-"))
+#   str(cleaned_fashion_tones$clean_date)
 
@@
 
-### Clean Fashion Frequency Data Set: 
-cleaned_fashion_frequency<-
-  clean_names(fashion_frequency)
-
-cleaned_fashion_frequency <-
-  cleaned_fashion_frequency |>
-  rename(
-    skintone = tone,
-    lightness_value = l,
-    num_covers = n_covers
-  )
+# ### Clean Fashion Frequency Data Set: 
+# cleaned_fashion_frequency<-
+#   clean_names(fashion_frequency)
+# 
+# cleaned_fashion_frequency <-
+#   cleaned_fashion_frequency |>
+#   rename(
+#     skintone = tone,
+#     lightness_value = l,
+#     num_covers = n_covers
+#   )
 
@@
 ### Clean Makeup Shades Data Set:
-cleaned_makeup_shades <-
-  clean_names(makeup_shades)
-
-cleaned_makeup_shades<-
-  cleaned_makeup_shades |>
-  rename(
-    hue = h,
-    lightness = l,
-    saturation = s,
-    value = v,
-    hex_code = hex
-  )|>
-  mutate(lightness_value = lightness/100)
-
-cleaned_makeup_shades<-
-  cleaned_makeup_shades |>
-  filter(group == 0|group == 1|group == 2|group == 3|group == 4)
+# cleaned_makeup_shades <-
+#   clean_names(makeup_shades)
+# 
+# cleaned_makeup_shades<-
+#   cleaned_makeup_shades |>
+#   rename(
+#     hue = h,
+#     lightness = l,
+#     saturation = s,
+#     value = v,
+#     hex_code = hex
+#   )|>
+#   mutate(lightness_value = lightness/100)
+# 
+# cleaned_makeup_shades<-
+#   cleaned_makeup_shades |>
+#   filter(group == 0|group == 1|group == 2|group == 3|group == 4)
 
@@
 But the presence of black and brown women in these spaces has a significant impact.
+
 An example of this is in the beauty industry.

### 2023-04-19 scripts/01-download_data.R

@@ -14,7 +14,7 @@ library(tidyverse)
 library(here)
 library(dplyr)
 
-#There are three data sets used for this analysis. All three are data sets used
+#There are three data sets used for this analysis. All three are data sets used in
 # the Puddings Publications, specifically, Beauty Brawl and Colorism in High Fashion.
 #### Download data ####
 fashion_tones <-

### 2023-04-19 scripts/02-data_cleaning.R

@@ -1,26 +1,89 @@
 #### Preamble ####
-# Purpose: Cleans.... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Data: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Cleans all three data sets about inclusivity in the fashion industry
+# Author: Huda Sahaf
+# Data: Apr 12 2023
+# Contact: huda.sahaf@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites:-
+# Any other information needed? -
 
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
+library(janitor)
+library(dplyr)
+library(ggplot2)
+library(kableExtra)
+library(knitr)
+library(readr)
+library(RColorBrewer)
+library(here)
+library(scales)
 
 #### Clean data ####
-# [...UPDATE THIS...]
-raw_data <- read_csv("inputs/data/raw_data.csv")
+fashion_tones <- read_csv("inputs/data/fashion_tones.csv")
+fashion_frequency <- read_csv("inputs/data/fashion_frequency.csv")
+makeup_shades <- read_csv("inputs/data/makeup_shades.csv")
 
+### Clean Fashion Tones Data Set: 
+cleaned_fashion_tones <-
+  clean_names(fashion_tones)
 
+cleaned_fashion_tones <-
+  cleaned_fashion_tones |>
+  rename(
+    skintone = tone,
+    lightness_value = l
+  )
+head(cleaned_fashion_tones)
 
+### Simplifying Dates: Fashion Tones Dataset:
+cleaned_fashion_tones<-
+  cleaned_fashion_tones |>
+  separate(
+    col = date,
+    into = c("Month", "Day", "Year"),
+    sep = "/"
+  ) |>
+  mutate(cleaned_fashion_tones, clean_date = paste(Year, Month, Day, sep = "-"))
+str(cleaned_fashion_tones$clean_date)
+
+### Clean Fashion Frequency Data Set: 
+cleaned_fashion_frequency<-
+  clean_names(fashion_frequency)
+
+cleaned_fashion_frequency <-
+  cleaned_fashion_frequency |>
+  rename(
+    skintone = tone,
[…]

### 2023-04-19 outputs/paper/paper.qmd
Simulated data and tests

--- 2023-04-18 outputs/paper/paper.qmd
@@
 
-### Simplifying Dates: Fashion Tones Dataset:
+### Simplifying Dates: Fashion Tones Data Set:
 cleaned_fashion_tones<-

### 2023-04-19 scripts/00-simulate_data.R

@@ -1,19 +1,36 @@
 #### Preamble ####
-# Purpose: Simulates... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Data: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Simulates data about the bias in the industry
+# Author: Huda Sahaf
+# Date: April 12th 2023
+# Contact: huda.sahaf@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: -
+# Any other information needed? -
 
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
+library(tibble)
 
 #### Simulate data ####
-# [...ADD CODE HERE...]
+
+set.seed(250)
+
+simulated_beauty_data <-
+  tibble(
+    "Model" = c(1:250),
+    "Lightness_Value" = sample(
+      x = c(1:100) /100,
+      size = 250,
+      replace = TRUE),
+    
+    "Vogue Appearances" = sample(
+      x = c(1:10),
+      size = 250, 
+      replace = TRUE)
+    
+  )
+simulated_beauty_data
 
 
 

### 2023-04-19 scripts/04-test_data.R

@@ -1,15 +1,27 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Data: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Tests the simulated_beauty_data
+# Author: Huda Sahaf
+# Data: Apr 12 2023
+# Contact: huda.sahaf@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: -
+# Any other information needed? -
 
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
+
 
 #### Test data ####
+
+simulated_beauty_data$Lightness_Value|>
+  min()== "0.01"
+
+simulated_beauty_data$`Vogue Appearances`|>
+  min()== 1
+
+simulated_beauty_data$`Vogue Appearances`|>
+  max() == 10
+
+simulated_beauty_data$Lightness_Value|>
+  max() == 1

### 2023-04-19 outputs/paper/paper.qmd
Discussion Section

@@
   filter(group == 0|group == 1|group == 2|group == 3|group == 4)
+```
+# Introduction
 
-```
+The beauty industry has been a huge part of self-expression for the greater part of human history.
+The use of makeup and decorative clothing is not new, and while self-expression used to be more individualized, the commercialized and cultural nature of the industry leaves something to be said about the systems that are in place.
+It is a very large industry, consisting of fashion, makeup, skin and haircare, which are include both products and services.
+"In the United States alone, the beauty services sector employs over 670,000 people, and its job growth outlook is “faster than average” according to BLS data at a rate of 13% (2016-2026).
+According to a study, it was worth $532.43 billion in 2017 and is expected to reach a market value of $805.61 billion by 2023"[@market].
 
+The makeup industry specifically has seen a lot of growth with the arrival of Sephora and Ulta, large retailers who host the products of a variety of brands both low and high end.
+This has popularized the notion of "indie brands", who have gained popularity by prioritizing high quality ingredients and affordability, allowing more people access to better products.
+However, all aspects of the beauty space still remain hesitant to uplift and empower people of all walks of life, especially people of color.
+The purpose of this paper is to explore the impact of the beauty industry's historically racist standards, and to explore whether they are still in place today.
+It is the fashion and makeup industry that will be the primary focus of this analysis.
+To explore racism in the fashion industry, the heart of the fashion culture, the covers of high fashion magazine Vogue, will be studied.
+The complexions of the models on the Vogue covers from 2000 to 2018 will be analyzed in order to extrapolate the inclusivity of the future of fashion.
+To analyze the makeup industry, the most popular foundation lines of the top beauty brands in the United States will be studied to explore the distribution of shades across the various complexions to see how many people of color are supported and provided for.
+
+# Data {#sec-data}
+## Data Management
+All analysis on the data sets were done using R [@citeR].
+The data was read in, cleaned, and manipulated using `dplyr`[@dan], `tidyverse` [@tidy], `arrow`[@adam] and `janitor` [@janice].
+The graphs and tables in this paper were coded using the following packages: `ggplot2` [@gabe], `kableExtra`[@kev], `knitr` [@nat], `readr` [@ron], and `RColorBrewer`[@ryan].
+
+## Source and Sampling
+In order to conduct an analysis on the various parts of the beauty industry, three separate data sets were used.
+The Pudding is a digital publication that makes its data sets open to the public @pudd.
+A closer look is taken at Vogue using the first two data sets used for the article *Colorism in High Fashion* [@high_f].
+All covers of Vogue from the year 2000 to 2018 are analyzed and categorized in these data sets.
+The female models on each cover are identified, and then their skin tones are filtered out of the cover, and an average color value is assigned based on the all skin tone pixels.
+These color values are then drained of any hue or saturation and therefore assigned a lightness value based on how light or deep the complexion of the model is, which allows for the comparison of all models on the covers of Vogue over the span of 8 years.
+The first data set contains the name of the model, date of their appearance on Vogue, the hex code of their skin tone, and their lightness value once the hue and saturation has been removed.
+This includes multiple appearances of the same model.
+The second data set contains the names of the models, the hex code of their skin tone, the number of covers they have made appearances in, and their average lightness value across these appearances.
+
+The data set behind The Pudding article, *Beauty Brawl* is the third data set used in this paper [@bbshades].
+It contains data about the foundation shade ranges through lightness values of multiple beauty brands around the world.
+For the sake of this paper, we are focusing on beauty retailers based in the US, especially since Vogue is also based in the United States.
+
+##Key Features:
+This paper explores the estimand how does the depth of your complexion impact your representation and the products made available for you in the fashion and makeup industry.
+This is explored through the lightness or complexion value.
+The hues and saturation are removed skin tones to get an idea of how light or dark a complexion is in order to assign it a value from 0 to 1, zero being the deepest complexion, and 1 being the palest.
+The fashion data sets contain data from 96 Vogue covers over the span of an 8 year period.
+The same lightness value is assigned to the various foundation shades offered by some of the biggest brands in the United states.
+The makeup data set contains data about the foundation lines of 16 major beauty brands in America.
+
+# Results
+@fig-fullspread is a graph of the lightness value of every model that has been on the cover of Vogue from 2000 to 2018.
+Lightness value is measured on a scale from 0 to 1, 1 being extremely pale in skin tone, and 0 being extremely deep.
+There is a general trend present almost immediately, in that across the entire 8 year period, Vogue has consistently had lighter skinned individuals with a lightness value of 0.5 to 0.8 on their covers.
+It has only been after around 2009 that we see a model on Vogue with a complexion deeper than 0.4.
 ```{r}
@@
   )
+```
 
-```
+@tbl-appearances is a table of all the models on Vogue who have had more than 4 appearances on the covers of Vogue between 2000 and 2018.
+In all of the names on this list, Rihanna is the only black woman, and her average lightness value across these five appearances has been fairly mid-toned, at a lightness value of 0.62.
 
@@
   geom_point()+
+  theme_minimal() +
   labs(
@@
   )
+```
 
-```
+@fig-whitewashing takes a closer look at Vogue's presentation of Rihanna's skin tone on her five appearances.
+Vogue has been publicly accused of whitewashing Rihanna's complexion on some of her covers, and it is apparent that only after 2016 does her lightness value drop below 0.4 [@whitewashed].
+While lighting and editing can account for some fluctuations in the lightness value, but it does not explain the extent of the contrast between her first three appearances and her most recent two.
 
@@
 
+@fig-deepest takes a closer look at the fluctuations in lightness values in the appearances on the models with the deepest complexions on Vogue.
+Rihanna has had the highest number of appearances at 5 total covers from 2000 to 2018, followed by Lupita Nyongo, at 4.
+Among these models, Lupita Nyongo has the deepest complexion and her appearances on Vogue are the most recent, her last two being in 2015 and in 2018.
+The fluctuation is apparent in her appearances as well, in that it is only in her most recent cover that her lightness value is shown to be deeper than 0.3.
+
 ```{r}
@@
 ```
+
+@fig-all_white shows the fluctuation in the lightness values of the top four models with the greatest number of covers on Vogue.
+All four of these models are white, and all of them have made appearances in 6 or more covers.
+Vogue's preferences for tanned white women is clear in that in the span of 8 years, the lightness value rarely drops below 0.6.
 
@@
 
+@tbl-shades is a table of all of the major beauty brands that are based in the United States, and the number of shades in their main foundation line.
+
 ```{r}
@@
   stat_ecdf(geom = "point") +
-  theme_classic()
+  theme_minimal()+ 
+  labs(
+    x = "Lightness Value of Skintone",
+    title = "The Shade Distribution of US Bestselling Foundation Lines",
+    color = "Brand"
+    )
 
 ```
+
+@fig-bestsellers takes a closer look at the inclusivity of the bestselling foundation lines across some of the largest beauty brands across the United States of America.
+It is clear that there are a greater number of shades available for people with lighter skin tones, with a lightness value of 0.6 or lighter, across all of the major brands.
+However, for people with a complexion that is a hair deeper than a medium skin tone, the number of shades become sparse, and the distribution spreads out as the lightness value becomes deeper than 0.5.
 ```{r}
@@
   stat_ecdf(geom = "point") +
-  theme_classic()
+  theme_minimal()+
+  labs(
+    x = "Lightness Value of Skintone",
+    title = "The Shade Distribution of Top BiPOC-Owned Foundations",
+    color = "Brand"
+    )
 ```
+
+@fig-bipoc looks at the shade distributions of the retailers with owners that are black, indigenous, or other people of color.
+The distribution is much more even, and all of these beauty brands provide options for people that are on both sides of the spectrum, complexions with lightness values deeper than 0.3, as well as complexions with lightness values paler than 0.8.
 
@@
   geom_jitter(alpha = 0.3, width = 0.15, height = 0) +
-  theme_minimal()
+  theme_minimal() +
+  labs(
+    x = "Brand",
+    y = "Lightness Value of Skintone",
+    title = "The Shade Distribution of Largest Foundation Shade Ranges Sold in the US"
+    )
 
 ```
-
-# Introduction
-
-You can and should cross-reference sections and sub-sections. For instance, @sec-data and @sec-first-point.
-
-# Data {#sec-data}
-## Data Management
-All analysis on the data sets were done using R [@citeR].
-The data was read in, cleaned, and manipulated using `dplyr`[@dan], `tidyverse` [@tidy], and `janitor` [@janice].
-The graphs and tables in this paper were coded using the following packages: `ggplot2` [@gabe], `kableExtra`[@kev], `knitr` [@nat], `readr` [@ron], and `RColorBrewer`[@ryan].
-
-## Source and Sampling
-In order to conduct an analysis on the various parts of the beauty industry, three separate data sets were used.
-The Pudding is a digital publication that makes its data sets open to the public @pudd.
-A closer look is taken at Vogue using the first two data sets used for the article *Colorism in High Fashion* [@high_f].
-All covers of Vogue from the year 2000 to 2018 are analyzed and categorized in these data sets.
-The female models on each cover are identified, and then their skin tones are filtered out of the cover, and an average color value is assigned based on the all skin tone pixels.
-These color values are then drained of any hue or saturation and therefore assigned a lightness value based on how light or deep the complexion of the model is, which allows for the comparison of all models on the covers of Vogue over the span of 8 years.
-The first data set contains the name of the model, date of their appearance on Vogue, the hex code of their skin tone, and their lightness value once the hue and saturation has been removed.
-This includes multiple appearances of the same model.
-The second data set contains the names of the models, the hex code of their skin tone, the number of covers they have made appearances in, and their average lightness value across these appearances.
-
-The data set behind The Pudding article, *Beauty Brawl* is the third data set used in this paper [@bbshades].
-It contains data about the foundation shade ranges through lightness values of multiple beauty brands around the world.
-For the sake of this paper, we are focusing on beauty retailers based in the US, especially since Vogue is also based in the United States.
-
-```{r}
-#| label: fig-bills
-#| fig-cap: Bills of penguins
-#| echo: false
-```
-
-# Results
-@fig-fullspread is a graph of the lightness value of every model that has been on the cover of Vogue from 2000 to 2018.
-Lightness value is measured on a scale from 0 to 1, 1 being extremely pale in skin tone, and 0 being extremely deep.
-There is a general trend present almost immediately, in that across the entire 8 year period, Vogue has consistently had lighter skinned individuals with a lightness value of 0.5 to 0.8 on their covers.
-It has only been after around 2009 that we see a model on Vogue with a complexion deeper than 0.4.
-
-@tbl-appearances is a table of all the models on Vogue who have had more than 4 appearances on the covers of Vogue between 2000 and 2018.
-In all of the names on this list, Rihanna is the only black woman, and her average lightness value across these five appearances has been fairly midtoned, at a lightness value of 0.62.
-
-@fig-whitewashing takes a closer look at Vogue's presentation of Rihanna's skintone on her five appearances.
-Vogue has been publicly accused of whitewashing Rihanna's complexion on some of her covers, and it is apparent that only after 2016 does her lightness value drop below 0.4 [@whitewashed].
-While lighting and editing can account for some fluctuations in the lightness value, but it does not explain the extent of the contrast between her first three appearances and her most recent two.
-
-@fig-deepest takes a closer look at the fluctuations in lightness values in the appearances on the models with the deepest complexions on Vogue.
-Rihanna has had the highest number of appearances at 5 total covers from 2000 to 2018, followed by Lupita Nyongo, at 4.
-Amongst these models, Lupita Nyongo has the deepest complexion and her appearances on Vogue are the most recent, her last two being in 2015 and in 2018.
-The fluctuation is apparent in her appearances as well, in that it is only in her most recent cover that her lightness value is shown to be deeper than 0.3.
-
-@fig-all_white shows the fluctuation in the lightness values of the top four models with the greatest number of covers on Vogue.
-All four of these models are white, and all of them have made appearances in 6 or more covers.
-Vogue's preferences for tanned white women is clear in that in the span of 8 years, the lightness value rarely drops below 0.6.
-
-@tbl-shades is a table of all of the major beauty brands that are based in the United States, and the number of shades in their main foundation line.
-
-@fig-bestsellers takes a closer look at the inclusivity of the bestselling foundation lines across some of the largest beauty brands across the United States of America.
-It is clear that there are a greater number of shades available for people with lighter skin tones, with a lightness value of 0.6 or lighter, across all of the major brands.
-However, for people with a complexion that is a hair deeper than a medium skin tone, the number of shades become sparse, and the distribution spreads out as the lightness value becomes deeper than 0.5.
-
-@fig-bipoc looks at the shade distributions of the retailers with owners that are black, indigenous, or other people of color.
-The distribution is much more even, and all of these beauty brands provide options for people that are on both sides of the spectrum, complexions with lightness values deeper than 0.3, as well as complexions with lightness values paler than 0.8.
 
@@
 
-## First discussion point {#sec-first-point}
+## Scarcity in the Beauty Industry {#sec-first-point}
 
@@
 
-## Second discussion point
+## Idealistic Beauty Standards
 
-## Third discussion point
+According to @fig-fullspread, there is a very gradual shift of a great number of appearances on Vogue of models with complexions that are deeper than 0.5, but it only recently in 2018, with Lupita Nyongo's cover with Vogue in 2018, that we see a model with a much deeper complexion than what is the norm for Vogue.
+According to @fig-bestsellers, a very similar trend is visible in that in the top 6 bestselling foundation brands in the United states, the number of shades providing for people of color is disappointingly sparse in comparison to the number of foundation shades offered for people who have a skin tone paler than a lightness value of 0.6.
+
+The fact of the matter is, there is a hierarchy present from light to dark.
+Even amongst black people, the deeper their complexion the more push back they recieve from the beauty industry.
+The issue with this, is that it creates an idealistic beauty standard.
+No matter where you are on the spectrum of complexions, you are encouraged to be paler in order to fit in.
+This is idealistic and racist standard is propped up by microaggressions all over the beauty industry, as well as in society overall.
+"We found 130 products on Sephora’s and Ulta’s websites that use a sequential number system to label their shades.
+Of those, 97% put their lighter shades, and thus the customers that use those shades, first.."[@truth].
+The way that beauty products are named, the way that they are displayed, the amounts of lighter shades that retailers keep in stock, all of these systems prioritize people with lighter skin.
+The problem with the way racism is addressed today is that all of these efforts are based in public apologies and pretty speeches.
+There are systems that are in place that uphold the racist standard, and when we apply these standards to women of color, some of the most disenfranchised groups in society, no amount of pretty speeches will heal a problem that has been hundreds of years in the making.
+The hierarchy that exists that pushes this standard of acceptability within society based on how pale or deep you are has the power to further divide people, and it is only right to question who stands to gain from this.
+
+## The Compounding Effect of Racism
+
+It is interesting to note that within the black models, featured on Vogue, the same people are featured multiple times, and the number of black women Vogue does not grow very much over time.
+It is the journey of getting to where lighter-skinned people are naturally that is frustratingly difficult.
+"Addressing racial inequity in the beauty industry is a $2.6 billion opportunity [@billion]".
+The black consumer base is there, there is a need for better products for black women and women of color, and yet there is so much more to addressing the racism in the industry than meets the eye.
+@fig-bestsellers look at the distribution of the foundation shade ranges of the best selling brands in the United States of America.
+@fig-bipoc takes a closer look at the efficiency and inclusivity of the shade distributions when the owner/CEO is black, indigenous, or woman of color.
+The difference between the two distributions are drastic, highlighting the power and all encompassing benefit of having a woman of color in a senior leadership position in the industry.
+
+The problem is, beauty products from black owned brands are not making enough to survive in the industry.
+The lack of representation translates to the business side of the beauty industry as well.
+There is very limited selection in drugstores and department stores, making it very difficult for the customer to even get access to these products in the first place.
+It is even more diffult for Black-owned businesses to gain a share of the market.
+As a result, they cannot get access in order to develop a loyal base of customers.
+There are no studies done on the needs of people of color, so business owners struggle to validate the need for their brand in the industry.
+It is harder to build a supportive network of individuals to support a business owner on the entrepreneurial journey.
+On every step of the way, black womena and women of color face obstacles that threaten their success.
+It is a system that needs to be addressed on the institutional level, which means that all major institutions need to put systems in place to support these women on every level, media and representation, marketing, research, and business.
 
 ## Weaknesses and next steps
-
-Weaknesses and next steps should also be included.
 

### 2023-04-19 scripts/01-download_data.R

@@ -13,6 +13,7 @@ library(readr)
 library(tidyverse)
 library(here)
 library(dplyr)
+library(arrow)
 
 #There are three data sets used for this analysis. All three are data sets used in
 # the Puddings Publications, specifically, Beauty Brawl and Colorism in High Fashion.
@@ -38,7 +39,7 @@ makeup_shades <-
 #### Save data ####
 
 write_csv(fashion_tones, here::here("inputs/data/fashion_tones.csv")) 
-
+write_parquet(fashion_tones, here::here("inputs/data/fashion_tones.parquet"))
 write_csv(fashion_frequency, here::here("inputs/data/fashion_frequency.csv")) 
 
 write_csv(makeup_shades, here::here("inputs/data/makeup_shades.csv")) 

### 2023-04-19 outputs/paper/paper.qmd
Limitation section

@@
 There is very limited selection in drugstores and department stores, making it very difficult for the customer to even get access to these products in the first place.
-It is even more diffult for Black-owned businesses to gain a share of the market.
+It is even more difficult for Black-owned businesses to gain a share of the market.
 As a result, they cannot get access in order to develop a loyal base of customers.
@@
 It is harder to build a supportive network of individuals to support a business owner on the entrepreneurial journey.
-On every step of the way, black womena and women of color face obstacles that threaten their success.
+On every step of the way, black women and women of color face obstacles that threaten their success.
 It is a system that needs to be addressed on the institutional level, which means that all major institutions need to put systems in place to support these women on every level, media and representation, marketing, research, and business.
@@
 
+There are a few weaknesses and limitations in this paper.
+Firstly, our analysis only covers representation in fashion culture and the range of products available in the makeup industry.
+Analysis can and should be done in other areas of the beauty industry, on both the product and service side.
+Secondly, there are limitations in the calculation of the lightness value.
+It does not include the various undertones in skin, and difference in makeup products and ingredients needed for people with deeper complexions.
+It is often the case that while some brands may offer foundation shades that are darker, but that does not mean that those shades are usable.
+Lack of research on the needs of people of color that often results in foundation shades that are the wrong undertone, too grey, orange, or red.
+The same goes for the lightness value calculation off of the Vogue covers.
+Vogue covers are heavily edited, with a team behind them for camera work, lighting, and editing.
+This could have skewed the depth of the complexion of the deeper skinned models, since according to @fig-all_white, there is a great deal of fluctuation in the skin tone to get an accurate understanding.
+Next steps would include using the hex code of the models foundation shade to get a more accurate representation of skin tone.
+
 \newpage

### 2023-04-19 outputs/paper/paper.qmd
final edits
final adjustments to the intro and references

@@
 The complexions of the models on the Vogue covers from 2000 to 2018 will be analyzed in order to extrapolate the inclusivity of the future of fashion.
-To analyze the makeup industry, the most popular foundation lines of the top beauty brands in the United States will be studied to explore the distribution of shades across the various complexions to see how many people of color are supported and provided for.
+To analyze the makeup industry, the most popular foundation lines of the top beauty brands in the United States will be studied to explore the distribution of shades across the various complexions to see how many people of color are supported and provided for.This paper explores the estimand how does the lightness value of an individuals complexion impact your representation and the products made available for you in the fashion and makeup industry.
 
@@
 There are a few weaknesses and limitations in this paper.
-Firstly, our analysis only covers representation in fashion culture and the range of products available in the makeup industry.
+Firstly, the analysis only covers representation in fashion culture and the range of products available in the makeup industry.
 Analysis can and should be done in other areas of the beauty industry, on both the product and service side.

### 2023-04-23 outputs/paper/paper.qmd

--- 2023-04-19 outputs/paper/paper.qmd
@@
 However, all aspects of the beauty space still remain hesitant to uplift and empower people of all walks of life, especially people of color.
+
 The purpose of this paper is to explore the impact of the beauty industry's historically racist standards, and to explore whether they are still in place today.
@@
 To analyze the makeup industry, the most popular foundation lines of the top beauty brands in the United States will be studied to explore the distribution of shades across the various complexions to see how many people of color are supported and provided for.
+This paper explores the estimand how does the lightness value of an individuals complexion impact your representation and the products made available for you in the fashion and makeup industry.
 
 # Data {#sec-data}
+
 ## Data Management
+
 All analysis on the data sets were done using R [@citeR].
@@
 ## Source and Sampling
+
 In order to conduct an analysis on the various parts of the beauty industry, three separate data sets were used.
@@
 
-##Key Features:
+## Key Features
+
 This paper explores the estimand how does the depth of your complexion impact your representation and the products made available for you in the fashion and makeup industry.
@@
 # Results
+
 @fig-fullspread is a graph of the lightness value of every model that has been on the cover of Vogue from 2000 to 2018.
@@
   ggplot(aes(x = lightness_value, y = clean_date)) +
-  geom_point(aes(color = lightness_value < 0.4)) + 
+  geom_point(aes(color = lightness_value < 0.4), alpha = 0.5) + 
   labs(
@@
     y = "Date of Cover",
-    title = "Complexions of Models on Covers of Vogue: 2000-2018"
+    title = "Complexions of Models on Covers of Vogue: 2000-2018",
+    color = "Lightness is <0.4?"
   ) +
@@
 #| echo: false
-#| tbl-cap: "Models With More than 5 Appearances on Vogue"
+#| tbl-cap: "Models With More than five Appearances on Vogue"
 #| label: tbl-appearances
@@
     ),
-    digits = 2
+    digits = 2,
+    booktabs = TRUE,
+    linesep = ""
   )
@@
       "Number of Foundation Shades"
-      )
+      ),
+        booktabs = TRUE,
+    linesep = ""
   )
@@
   ggplot(aes(x = lightness_value, color = brand)) +
-  stat_ecdf(geom = "point") +
+  stat_ecdf(geom = "point", alpha = 0.6) +
   theme_minimal()+ 
@@
     x = "Brand",
-    y = "Lightness Value of Skintone",
-    title = "The Shade Distribution of Largest Foundation Shade Ranges Sold in the US"
-    )
+    y = "Lightness Value of Skintone"
+    ) + 
+  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
 
